\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-22 draft.tex
rewrite first half of prop:2NNB proof in draft

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}
\usepackage[pdftex]{graphicx}
%\usepackage{pdfpages}

@@

@@

\section*{Appendix}
\label{sec:app}
\pdfbookmark{Appendix}{sec:appendix}
\noindent \textbf{\hypertarget{Pr_2NNB}{Proof of Proposition~\ref{prop:2NNB}}}: \\
Without loss of generality, assume that it is the legislators at $-\frac{1}{2}$ and $0$ that are bribed. The first order conditions with respect to the bribes for these two legislators are
	\begin{equation}
		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
	\end{equation}
	and
	\begin{equation}
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
		\label{eq:base}
	\end{equation}

		Setting the left-hand size of these two equations equal to each other and simplifying,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\[
		  e^{Y-Z} - e^{X-Z}= e^{-X} - e^{-Y}
		\]
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}

@@

\vskip.2in
\noindent \un{Second Order Conditions} \\
When one non-negativity constraint binds, the bordered Hessian is 4x4.\\
		$\left|\begin{tabular}{cccc}
			0 & $\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ \\
			$\frac{\partial g_1}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
			$\frac{\partial g_1}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
			$\frac{\partial g_1}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
		\end{tabular} \right|\\$
$\hfill\blacksquare$

>>>>

\usepackage[pdftex]{graphicx}
%\usepackage{pdfpages}

@@

\usepackage[pdftex,
bookmarks=true,
bookmarksnumbered=false,
pdfview=fitH,
bookmarksopen=true]{hyperref}

@@

\section*{Appendix}
\label{sec:app}
\pdfbookmark{Appendix}{sec:appendix}
\noindent \textbf{\hypertarget{Pr_2NNB}{Proof of Proposition~\ref{prop:2NNB}}}: \\
Without loss of generality, assume that it is the legislators at $-\frac{1}{2}$ and $0$ that are bribed. The first order conditions with respect to the bribes for these two legislators are
	\begin{equation}
		\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\label{eq:baseY}
	\end{equation}
	and
	\begin{equation}
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
		\label{eq:base}
	\end{equation}

		\vskip.2in
The second derivative, for instance with respect to $b_0$ is
\begin{equation}
  \frac{\partial^2 L}{\partial b(0)^2} = W_B\left[\frac{e^{-Z} + e^{-Y}}{\left(1+e^{-Z}\right)\left(1+e^{-Y}\right)} \right] \left[ \frac{e^{-X}}{\left(1+e^{-X}\right)^3} \right] \left\{e^{-X}-1 \right\}
	\label{eq:secderiv}
\end{equation}
Everything except for the expression in the curly braces is positive. The expression in the curly braces is positive when $X<0$ and negative when $X>0$. It is zero when $X=0$. Analogous expressions hold for the second derivatives with respect to $b_{-.5}$ and $b_{.5}$.

\vskip.2in
The cross partials are of the form 
\begin{equation}
  \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} = W_B\frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}\left[\frac{e^{-X}\left(e^{-2Z} - 1 \right)}{\left(1+e^{-X}\right)^2\left(1+e^{-Z}\right)^2} \right]
	\label{eq:xpartial}
\end{equation}
The sign of this expression is the same as the sign of $e^{-2Z} - 1$. It's 0 when $Z=0$, positive when $Z < 0$ and negative when $Z > 0$.

When one non-negativity constraint binds, the bordered Hessian is 4x4. \\
		$\left|\begin{tabular}{cccc}
			0 & $\frac{\partial g_3}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial g_3}{\partial b_{\frac{1}{2}}}$ \\
			$\frac{\partial g_3}{\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}^2}$ & $\frac{\partial^2 L}{\partial b_0\partial b_{-\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}} \partial b_{-\frac{1}{2}}}$  \\
			$\frac{\partial g_3}{\partial b_0}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}} \partial b_0}$ & $\frac{\partial^2 L}{\partial b_0^2}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}\partial b_0}$ \\
			$\frac{\partial g_3}{\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{-\frac{1}{2}}\partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_0 \partial b_{\frac{1}{2}}}$ & $\frac{\partial^2 L}{\partial b_{\frac{1}{2}}^2}$
		\end{tabular} \right|\\$

Evaluating the constraint terms, we have\\
\begin{tabular}{cccc}
			0 & 0 & 0 & -1 \\
			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
		\end{tabular}

\vskip.2in
The second order condition is on the last two principal minors. The largest must be negative. The next to last should then be positive.

The next-to-last principal minor is the 3x3 matrix that is the upper-lefthand corner of this matrix. This determinant should be non-negative but is identically equal to zero because of the first row of zeros. This therefore provides no restrictions on the problem.\footnote{In the case where it is the non-negativity constraint on either $b_0$ or $b_{-.5}$ that binds, this condition \textit{does} imply an extra constraint. When $b_0 = 0$, the extra constraint is that $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq0$, i.e. $Y\leq 0$. When $b_{-.5}=0$, the extra condition is that $X\leq 0$.}
\begin{itemize}
	\item Second, we need the determinant of the last principal minor, which is the whole 4x4 matrix. This determinant can be simplified as follows:
		\[
		  0 \cdot \left|\text{something} \right| - 0 \cdot \left|\text{something} \right| + 0 \cdot \left|\text{something} \right| - (-1)\cdot 
			\left|\begin{array}{ccc}
				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
			\end{array} \right| 
		\]
		\[ 
			=
			\left|\begin{array}{ccc}
				0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}  \\
			0 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} & \frac{\partial^2 L}{\partial b(0)^2} \\
			-1 & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}& \frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)} 
			\end{array} \right| 
		\]
		\[
		  = - 1 \cdot \left|\begin{array}{cc}
			\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} & \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)} \\
			\frac{\partial^2 L}{\partial b(0) \partial b\left(-\frac{1}{2}\right)} & \frac{\partial^2 L}{\partial b(0)^2}
			\end{array} \right|
		\]
		\[
		  = - 1 \cdot \left(
			\frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} - \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 \right)
		\]
		\[
		  = \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 - \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}
		\]

  We need this determinant to be non-positive, that is
		\begin{equation}
		  \frac{\partial^2 L}{\partial b(0)^2} \frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2} \geq \left[\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}\right]^2 
			\label{eq:soc}
		\end{equation}
	  The right hand side is non-negative because it's a square. The left hand side must then be non-negative. 
\end{itemize}

\vskip.5in
		Setting the left-hand size of these two equations equal to each other and simplifying,
		\[
		  \frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Y} + e^{-X-Z}}{1+e^{-X}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Y} + e^{-X-Z} + e^{-X-2Y} +e^{-X-Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-2X-Y} +e^{-X-Y-Z}
		\]
		\[
		  e^{-X-Z} +e^{-X-2Y}= e^{-Y-Z} +e^{-2X-Y}
		\]
		\[
		  e^{-Z} +e^{-2Y}= e^{X-Y-Z} +e^{-X-Y}
		\]
		\begin{equation}
		  e^{Y-Z} +e^{-Y}= e^{X-Z} +e^{-X}
			\label{eq:twoways}
		\end{equation}
   Equation~\ref{eq:twoways} can be rearranged into two similar forms. First:
		\begin{equation}
		  e^{Y} - e^{X}= e^Z\left(e^{-X} - e^{-Y}\right)
			\label{eq:1}
		\end{equation}
  	Second, multiplying through by zero:
	  \begin{equation}
		  e^{X} - e^{Y}= e^Z\left(e^{-Y} - e^{-X}\right)
			\label{eq:2}
		\end{equation}

@@

$\hfill\blacksquare$
